---
title: "Test 1"
author: "SB Galvin"
date: "17 December 2018"
output: 
  html_document:
    df_print: paged
---
# Introduction
This is a test file to see if GitHub still renderd .Rmd files. Code using dplyr chains with the pipe operator ` %>% `

# Options
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(stringsAsFactors = FALSE,
        scipen = 999)
set.seed(42)
library(tidyverse)
```


# One
Make some data
```{r}
test_df  <-  data.frame(x = rnorm(1000, 99, 15),
                        y = rnorm(1000, 101, 15))
```

Show the dataframe  
```{r}
test_df
```

The columns are two different groups. The rows are not unique cases.

# Two
Wide data to long data
The columns are two different groups. The rows are not unique cases.
```{r}
test_df %>% 
  
  # wide to long
  gather(Group, Response, x:y) ->> test_df_long
```

Show the new df
Each column is a variable, each row is an observation
```{r}
test_df_long
```


## ggplot2
This is just a quick 
```{r}
test_df_long %>% 
  ggplot(aes(x = Response, fill = Group))+
  geom_histogram(colour="white")+
  facet_wrap(~Group)+
  theme_minimal()
```
