---
title: "Test 1"
author: "SB Galvin"
date: "17 December 2018"
output: 
  html_document:
    df_print: paged
---
# Introduction
This is a test file to see if GitHub still renderd .Rmd files. Code using dplyr chains with the pipe operator ` %>% `

# Options
Set the options for the file
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
options(stringsAsFactors = FALSE,
        scipen = 999)
set.seed(42)

library(effsize) # for Cohen's D
library(sjstats) # for omega squared
library(tidyverse) # for everything else # eg ggplot2, dplyr, magrittr pipe %>% 
```


# One
Make some data
```{r}
test_df  <-  data.frame(x = rnorm(1000, 99, 15),
                        y = rnorm(1000, 101, 15))
```

Show the dataframe  
```{r}
test_df
```

The columns are two different groups. The rows are not unique cases.

# Two
Wide data to long data
The columns are two different groups. The rows are not unique cases.
```{r}
test_df %>% 
  
  # wide to long
  gather(Group, Response, x:y) ->> test_df_long
```

Show the new df
Each column is a variable, each row is an observation
```{r}
test_df_long
```


## ggplot2
This is just a quick test 
```{r, fig.align='center'}
test_df_long %>% 
  ggplot(aes(x = Response, fill = Group))+
  geom_histogram(colour="white")+
  facet_wrap(~Group)+
  theme_minimal()
```

A summary table
```{r}
test_df_long %>% 
  # pipe to the groupby function
  # further functions while be applied to data grouped by the Group argument
  group_by(Group) %>% 
  # Summarise the data
  # Assign a name to a result using =
  # mean
  summarise(Mean = mean(Response),
            # Standard Deviation
            StDev = sd(Response),
            # Count of observations per group
            N = n(),
            # Standard Error
            StErr = (StDev/sqrt(N)),
            # 95% Lower Bound Confidence Interval
            lwrBound = Mean - (StErr * 1.96),
            # 95% Upper Bound Confidence Interval
            uprBound = Mean + (StErr * 1.96)) ->> df_summary # output object
# print the output object in rmd file
df_summary
```


```{r}
# Pass the dataframe as the data argument to ggplot()
ggplot(data = test_df_long,
       # Set the aesthetics layer
       # x is variable of interest
       # fill sets the colour option
       aes(x = Response, fill = Group))+
  geom_histogram(colour="white")+
  
  # Error bars
  # X error bars (in horizontal position)
  # values generated using a summary table
  # 95% SE conf int.
  # y is set to an arbitrary value
  geom_errorbarh(aes(y = 100, 
                     # minimum value
                     xmin = 97.68,
                     xmax = 99.54),
                 # sets the height of the error bars
                 height = 8)+
  # y error bars (in horizontal position)
  # values generated using a summary table
  # 95% SE conf int.
  # y is set to an arbitrary value
  geom_errorbarh(aes(y = 80, 
                     # min value
                     xmin = 100.00,
                     # max value
                     xmax = 101.84),
                 # sets height of the error bars
                 height = 8)+
  # X mean
  # generated using the point geometry
  # y is set to an arbitrary value, same as line 16
  geom_point(aes(y = 100, x = mean(test_df_long[Group=="x",]$Response)),
             # Sets point colour to white
             colour = "white")+
  # Y mean
  # generated using the point geometry
  # y is set to an arbitrary value, same as line 26
  geom_point(aes(y = 80, x = mean(test_df_long[Group=="y",]$Response)),
             # Sets point colour to white
             colour = "white")+
  # adds the minimal theme to the plot output
  theme_minimal()+
  # Places the legend at the top of the plot
  theme(legend.position = "top")
```

Violin plot
```{r}
ggplot(test_df_long, aes(x = Group, y = Response, fill=Group))+
  geom_violin()+
  # Plot a boxplot inside the violin
  geom_boxplot(fill='white', width=.3)+
  theme_minimal()
```

# Three
### t-test
Perform a two sample t-test
```{r}
model_t_test <- t.test(Response~Group, data = test_df_long)
```

#### t-test output
```{r}
model_t_test
```

#### effect size
using the `effsize` package
```{r}
effect_D <- cohen.d(Response ~ Group, data = test_df_long)
effect_D$estimate
```
#### Tidy

```{r}
# Create a summary of the t-test uisng tidy() from the broom package
broom::tidy(model_t_test) ->> tidy_t_test

# Assign cohens D to a column in the summary table
tidy_t_test$D <- effect_D$estimate # Cohens D
```
#### Present the table
```{r}
# Print the t-test output
tidy_t_test
```


We can see from the output that the effect size `D` is quite small `-0.1547178`

### Linear Model
```{r}
model_lm <- lm(Response~Group, data = test_df_long)
```

```{r}
summary(model_lm)
```
```{r}
model_lm$residuals ->> Resid_D

leftovers <- data.frame(id = seq(1:length(Resid_D)), Residuals = Resid_D)
                        
ggplot(leftovers,
       aes(x = Residuals))+
  geom_histogram(colour = "white")+
  # adds the minimal theme to the plot output
  theme_minimal()
```

```{r}
broom::tidy(model_lm) ->> lm_summary
```
```{r}
sjstats::omega_sq(model_lm) ->> Omega_SQ
sjstats::cohens_f(model_lm)
#Omega_SQ$
lm_summary$OMEGA  <- c("-", Omega_SQ$omegasq)
```

View the Summary table
```{r}
lm_summary
```

```{r}
test_df_long %>% 
  ggplot(aes(x = Group, y = Response))+
  geom_point(alpha = .3)+
  geom_abline(intercept = 98.61, slope = 2.3, size = 2,
              colour = "tomato",
              linetype = "dotted")+
  theme_minimal()
```

